pdp: An R Package for Creating Partial Dependence Plots

### 2016-09-07 manuscript/greenwell.tex
add ggplot2 reference

Currently, only two functions are exported by \pkg{pdp}:
\begin{itemize}
  \item \code{partial}
  \item \code{plotPartial}
\end{itemize}
The \code{partial} function evaluates the partial dependence \eqref{eqn:pdf} from a fitted model over a grid of predictor values; the predictors are specified using the \code{pred.var} argument. If \code{plot = FALSE} (the default), \code{partial} returns an object of class \code{"partial"} which inherits from the class \code{"data.frame"}; in other words, by default, \code{partial} returns a data frame with an additional class that is recognized by the \code{plotPartial} function. The columns are labeled in the same order as the features supplied to \code{pred.var}, and the last column is always labeled \code{y} and contains the values of the partial dependence function $\bar{f}_s\left(\boldsymbol{z}_s\right)$. If \code{plot = TRUE}, then \code{partial} makes an internal call to \code{plotPartial} and returns the PDP in the form of a \CRANpkg{lattice} plot \citep{lattice-pkg}. The \code{plotPartial} function can be used for displaying more advanced PDPs; it operates on objects of class \code{"partial"} and has many useful plotting options. Of course, since the default output produced by \code{partial} is still a data frame, the user can use any plotting package he/she desires to visualize the results.

>>>>

Currently, only two functions are exported by \pkg{pdp}:
\begin{itemize}
  \item \code{partial}
  \item \code{plotPartial}
\end{itemize}
The \code{partial} function evaluates the partial dependence \eqref{eqn:pdf} from a fitted model over a grid of predictor values; the predictors are specified using the \code{pred.var} argument. If \code{plot = FALSE} (the default), \code{partial} returns an object of class \code{"partial"} which inherits from the class \code{"data.frame"}; in other words, by default, \code{partial} returns a data frame with an additional class that is recognized by the \code{plotPartial} function. The columns are labeled in the same order as the features supplied to \code{pred.var}, and the last column is always labeled \code{y} and contains the values of the partial dependence function $\bar{f}_s\left(\boldsymbol{z}_s\right)$. If \code{plot = TRUE}, then \code{partial} makes an internal call to \code{plotPartial} and returns the PDP in the form of a \CRANpkg{lattice} plot \citep{lattice-pkg}. The \code{plotPartial} function can be used for displaying more advanced PDPs; it operates on objects of class \code{"partial"} and has many useful plotting options. Of course, since the default output produced by \code{partial} is still a data frame, the user can use any plotting package he/she desires to visualize the results--\CRANpkg{ggplot2} \citep{ggplot2-pkg}, for instance.
